---
title: "Initial Data Exploration"
output: html_notebook
---

# Data Exploration
Notebook to perform initial analysis on dataset contents and structure.

## Load Data and Analyse first few rows

```{r}
data <- read.csv("../data/raw/raw.csv", sep = ";")
head(data)
```

## Data Structures

```{r}
str(data)
```
## Data Summary

```{r}
summary(data)
```
## Categorical Variables

### Question Level
```{r}
unique(data$Question.Level)
```
### Topic
```{r}
unique(data$Topic)
```
### Subtopic
```{r}
unique(data$Subtopic)
```
### Keywords
```{r}
unique(data$Keywords)
```



# Conclusions

| Feature | Type | Notes |
|---------|------|-------|
| Student.ID | int | Identifier for Student |
| Student.Country | chr | |
| Question.ID | int | Identifier for Question |
| Type.of.Answer | int | Categorical as int: correct (0) vs incorrect (1) |
| Question.Level | chr |  Categorical: Difficulty of Question: Basic vs Advanced |
| Topic | chr | Categorical: Level 0 Math Topic |
| Subtopic | chr | Categorical: Level 1 Topic of Math Topic |  
| Keywords | chr | Categorical: Additional Contextual Information |
